---
title: "Practical Machine Learning Assignment"
author: "Zhong Qihui"
date: "11/09/2018"
output:
  html_document:
    df_print: paged
  word_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Loading packages

```{r loading,echo=TRUE}
library(caret)
library(randomForest)
library(parallel)
library(doParallel)
```

# Data pre-processing

Then, I need to import and clean the data.

```{r cleaning,echo=TRUE}
pml_train <- read.csv("https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv")
isTrainNA <- is.na(pml_train[1,])
newTrain <- pml_train[,isTrainNA==FALSE] # Deleting blank columns
isTrainBS <- newTrain[1,]==''
newTrain <- newTrain[,isTrainBS!=TRUE]
newTrain <- newTrain[,-c(1:7)] # Deleting the first 7 columns since they are useless
pml_test <- read.csv("https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv")
isTestNA <- is.na(pml_test[1,])
newTest <- pml_test[,isTestNA==FALSE] # Deleting blank columns
isTestBS <- newTest[1,]==''
newTest <- newTest[,isTestBS!=TRUE]
newTest <- newTest[,-c(1:7)] # Deleting the first 7 columns since they are useless
```

# Building the model

I choose to apply random forest algorithm. But before doing that, I should create a partition of my data.

```{r partition, echo=TRUE}
set.seed(1997)
inTrain <- createDataPartition(newTrain$classe,p=0.75,list=FALSE)
Training <- newTrain[inTrain,]; Testing <- newTrain[-inTrain,]
```

Now I can continue to build my model. I have chosen random forest algorithm, because I think its accuracy is high. Some parameters should be set before modelling so that efficiency could be improved.

```{r randomForest,echo=TRUE}
ctrl <- trainControl(method = "cv",number = 5,allowParallel=TRUE)
model <- train(classe ~ ., data = Training, method = "rf", trControl=ctrl,verbose=FALSE)
predict <- predict(model, newdata = Testing)
confusionMatrix(Testing$classe, predict)
plot(model$finalModel)
```

As we can see from the table. The accuracy is close to 1, which is very high.

# Prediction

Now we can use our model to predict the manner of 20 observations.
```{r prediction,echo=TRUE}
predict(model,newdata=newTest)
```
